---
title: "MIDN 2022 report figures and tables"
author: "Camilla Seirup"
date: "12/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.kable.NA = '')
```

```{r deps, include = FALSE}
library(tidyverse)
library(forestMIDN)
library(forestTrends)
library(htmltools)
library(knitr)
library(kableExtra)
```

```{r import, include = FALSE, cache = FALSE}
importCSV(path = 'C:/01_NETN/Forest_Health/R_Dev/MIDN_report', zip_name = 'MIDN_Forest_20211215.zip')
```

```{r compile_data, include = FALSE}
source("02_MIDN_2022_report_compile.R")
```

## {.tabset .tabset-pills}

### Regeneration Metrics {.tabset}
Only included live, native, canopy trees

#### Sapling Density
<h3>By cycle<h3>
```{r sap loess by cycle, echo=FALSE}
sapC
```

<h3>By year<h3>
```{r sap loess by year, echo=FALSE}
sapY
```


#### Seedling Density
<h3>By cycle<h3>
```{r seed loess by cycle, echo=FALSE}
seedC
```

<h3>By year<h3>
```{r seed loess by year, echo=FALSE}
seedY
```

#### By Size Class
```{r regen dist by size class, echo=FALSE}
regen_plot
```

Last 4 years of data:
"FRSP", "RICH", "PETE", "GEWA", "THST" -> last four years 2018 - 2021

"VAFO", "HOFU", "GETT", "APCO", "BOWA", "COLO", "SAHI", "ASIS") -> last four years 2016-2019

#### Sapling Diameter Distibution
```{r sap diameter dist, echo=FALSE}
sap_dist_plot
```


"FRSP", "RICH", "PETE", "GEWA", "THST" -> last four years 2018 - 2021

"VAFO", "HOFU", "GETT", "APCO", "BOWA", "COLO", "SAHI", "ASIS") -> last four years 2016-2019

### Deer Browse Index {.tabset}
```{r dbi, echo=FALSE}
DBI_plot
```

"FRSP", "RICH", "PETE", "GEWA", "THST" -> last four years 2018 - 2021

"VAFO", "HOFU", "GETT", "APCO", "BOWA", "COLO", "SAHI", "ASIS") -> last four years 2016-2019

Problem: DBI not collected until 2009 so MIDN plots cycle 1 only include 50% of plots and NCBN cycle 1 includes 75% of plots
ASIS, COLO, and SAHI cycle 1 are complete

### Stocking Index {.tabset}
#### Trend
<h3>By cycle (density in stems/m.sq)<h3>
```{r stock loess by cycle, echo=FALSE}
stockC
```

<h3>By year (density in stems/m.sq)<h3>
```{r stock loess by year, echo=FALSE}
stockY
```

#### Status
```{r stock status, echo=FALSE}
stkStatus
```

Mean stocking index for the last four years of sampling at each park

"FRSP", "RICH", "PETE", "GEWA", "THST" -> last four years 2018 - 2021

"VAFO", "HOFU", "GETT", "APCO", "BOWA", "COLO", "SAHI", "ASIS") -> last four years 2016-2019

#### Percent of Stocked Plots
```{r Percent of plots stocked, echo=FALSE}
pStk_plot
```

% of plots that were stocked after the last four years of sampling at each park

"FRSP", "RICH", "PETE", "GEWA", "THST" -> last four years 2018 - 2021

"VAFO", "HOFU", "GETT", "APCO", "BOWA", "COLO", "SAHI", "ASIS") -> last four years 2016-2019


### Tree Metrics {.tabset}
#### Basal Area
<h3>By cycle (basal area in m.sq/ha)<h3>
```{r BA loess by cycle, echo=FALSE}
TreeBA_C
```

<h5>"FRSP", "RICH", "PETE", "GEWA", "THST" -> last four years 2018 - 2021

"VAFO", "HOFU", "GETT", "APCO", "BOWA", "COLO", "SAHI", "ASIS") -> last four years 2016-2019<h5>

<h3>By year (basal area in m.sq/ha)<h3>
```{r BA loess by year, echo=FALSE}
TreeBA_Y
```

#### Density
<h3>By cycle (stems/ha)<h3>
```{r tree dens loess by cycle, echo=FALSE}
TreeDen_C
```

"FRSP", "RICH", "PETE", "GEWA", "THST" -> last four years 2018 - 2021

"VAFO", "HOFU", "GETT", "APCO", "BOWA", "COLO", "SAHI", "ASIS") -> last four years 2016-2019

<h3>By year (stems/ha)<h3>
```{r tree dens loess by year, echo=FALSE}
TreeDen_Y
```

#### Diameter Distibution
```{r tree diameter dist, echo=FALSE}
tree_dist_plot
```

Diameter distribution for live, native trees >10cm

"FRSP", "RICH", "PETE", "GEWA", "THST" -> last four years 2018 - 2021

"VAFO", "HOFU", "GETT", "APCO", "BOWA", "COLO", "SAHI", "ASIS") -> last four years 2016-2019


</div>